### 2019-12-27 paper.rmd
update GRoLTS checklist and present in a table in the paper
add GRoLTS items as headers

```{r, echo = FALSE}
t <- read_csv("GRoLTS-applicability-to-LPA.csv")
t
```

>>>>

```{r, echo = FALSE}
t <- read_csv("GRoLTS-applicability-to-LPA.csv")
tp <- t %>% 
  filter(use == 1) %>% 
  mutate(`LPA Number` = 1:nrow(.)) %>% 
  select(`GRoLTS Number` = Number, `LPA Number`, `Checklist Item`)

tp %>% 
  DT::datatable()
```

We walk through each of these in turn.

### Is the missing data mechanism reported?                                                                                                                                                                                                         
### Is a description provided of what variables are related to attrition/missing data?

### Is a description provided of how missing data in the analyses were dealt with?

### Is information about the distribution of the observed variables included?

### Is the software mentioned?

### Are alternative specifications of the between-class differences in variance–covariance matrix structure considered and clearly documented?

### Is information reported about the number of random start values and final iterations included?

### Are the model comparison (and selection) tools described from a statistical perspective?

### Are the total number of fitted models reported, including a one-class solution?

### Are the number of cases per class reported for each model (absolute sample size, or proportion)?

### If classification of cases in a trajectory is the goal, is entropy reported?

### Are all of the estimates plotted?

### Are the raw data plotted along with the estimates?

### Are characteristics of the final class solution numerically described (i.e., means, SD/SE, n, CI, etc.)?

### Are the syntax files available (either in the appendix, supplementary materials, or from the authors)?
